Methods for Large Scale Learning to Rank

### 2014-11-13 report/Chapters/Introduction.tex
weer dingen van Dolf :)

To research the speed-up's dependence on the amount of data that is being processed, the training computations will be performed on data sets of varying sizes. We use the well-known benchmark collections LETOR 3.0, LETOR 4.0 and MSLR-WEB30/40K as a starting set of data sets for our experiments. Table \ref{tbl:initial_datasets} shows the data sizes of these data sets. The data sizes reported are not the total on-disk sizes of the data sets, but instead the size of the largest training set of all data folds (for an explanation of the concept of data folds, see \ref{sec:cross_validation}).

@@

\section{Thesis Overview}
\begin{description}
\item[Chapter 2: Background]{introduces the reader to the basic principles and recent work in the fields of Learning to Rank and the MapReduce computing model. Aims at bringing those unfamiliar with those topics up to speed to be able to understand the succeeding chapters of this thesis.}
\item[Chapter 3: Related Work]{concisely describes existing work in the field of parallel and distributed Learning to Rank.}
\item[Chapter 4: Benchmark Data Sets]{described the characteristics of the existing benchmark data sets in the Learning to Rank field.}
\item[Chapter 5: Cross Benchmark Comparison]{described the methodology of a comparison of ranking accuracy of Learning to Rank methods across benchmark data sets and described the results of this comparison.}
\item[Chapter 6: Selected Learning to Rank Methods]{describes the algorithms and details of the Learning to Rank methods selected in Chapter V.}
\item[Chapter 7: Implementation]{describes implementation details of the Learning to Rank algorithms in the Hadoop framework.}
\item[Chapter 8: MapReduce Experiments]{presents and discusses speed-up results for the implemented Learning to Rank methods.}
\item[Chapter 9: Conclusions]{summarizes the results and answers our research questions based on the results. The limitations of our research as well as future research directions in the field are mentioned here.}
\item[Chapter 10: Future Work]{describes several directions of research worthy follow-up research based on our findings.}
\end{description}

>>>>

To research the speed-up's dependence on the amount of processed data, the training computations will be performed on data sets of varying sizes. We use the well-known benchmark collections LETOR 3.0, LETOR 4.0 and MSLR-WEB30/40K as a starting set of data sets for our experiments. Table \ref{tbl:initial_datasets} shows the data sizes of these data sets. The data sizes reported are not the total on-disk sizes of the data sets, but instead the size of the largest training set of all data folds (for an explanation of the concept of data folds, see \ref{sec:cross_validation}).

@@

\section{Thesis Overview}
\begin{description}
\item[Chapter 2: Background]{introduces the basic principles and recent work in the fields of Learning to Rank and the MapReduce computing model.}
\item[Chapter 3: Related Work]{concisely describes existing work in the field of parallel and distributed Learning to Rank.}
\item[Chapter 4: Benchmark Data Sets]{describes the characteristics of the existing benchmark data sets in the Learning to Rank field.}
\item[Chapter 5: Cross-Benchmark Comparison]{describes the methodology of a comparison of ranking accuracy of Learning to Rank methods across benchmark data sets and describes the results of this comparison.}
\item[Chapter 6: Selected Learning to Rank Methods]{describes the algorithms and details of the Learning to Rank methods selected in Chapter V.}
\item[Chapter 7: Implementation]{describes implementation details of the Learning to Rank algorithms in the Hadoop framework.}
\item[Chapter 8: MapReduce Experiments]{presents and discusses speed-up results for the implemented Learning to Rank methods.}
\item[Chapter 9: Conclusions]{summarizes the results and answers our research questions based on the results. The limitations of our research as well as future research directions in the field are mentioned here.}
\item[Chapter 10: Future Work]{describes several directions of research worthy follow-up research based on our findings.}
\end{description}
